Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
added figure 7 caption

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
	\caption{.}
	\label{fig:toy_sigloss16}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples. In red, the mock EoR signal is comprised entirely of independent samples. Subsequent colors show time-averaged signals. As the number of realizations increases, we see that the empirical covariances approach the true covariances. With more independent samples, the quicker an empirical covariance converges.}
	\label{fig:toy_sigloss16}
\end{figure}
